---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AmesPD

<!-- badges: start -->
[![R-CMD-check](https://github.com/Stat585-at-ISU/AmesPD/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Stat585-at-ISU/AmesPD/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of AmesPD is to filter and visualize service calls to the Ames Police Department (2021-2023) or ISU Police (2012-2019). We introduce a shiny app as an interactive way for users to filter these calls based on dates, types of incidents, locations, etc. 

## Installation

You can install the development version of AmesPD from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Stat585-at-ISU/AmesPD")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AmesPD)
## basic example code
```

There are two sources of data to choose from: Ames PD and ISU Police.

```{r cars}
head(presslog_ames)
head(presslog_isu)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure) # show an example plot here
```
